\section{Setup}


\begin{enumerate}

	\item  Suppose a physician can only observe an ATE and some measure of representativeness. Physicians have prior
		$\bar{\beta}$ and  $\beta_{ATE} = (1/N) \sum \beta_{i}$.

	\item We need a model for the betas related to each other based on $x$'s -- an individuals characteristics.

		Suppose
		\begin{align*}
			\beta(x_i) = x_i \gamma
		\end{align*} 
		Where $x_i$ is a vector of characteristics and $\gamma$ is a vector of coefficients. \\
		If you know $\gamma$, then you know $\beta$ for any given patient.
	\item However, you don't observe $\gamma$, you instead observe:
		$\beta_{ATE} = \bar x \gamma$ where $\bar x = (\frac{1}{N}) \sum x_i$
	\item We know $\beta_i$ for patients with characteristics $\bar x$ (it is $\beta_{ATE}$).
	\item For other patients, we need to solve
		\begin{align*}
			\beta_{i,post} = \E(x_i \gamma | \bar x \gamma = \beta_{ATE})
		\end{align*} 

	\item To solve
		\begin{enumerate}
			\item
				\begin{align*}
					\beta_{i,post} & = \E (x_i \gamma | \bar x \gamma = \beta_{ATE})                                                                        \\
								   & = \E((x_i - c_i \bar{x}) \gamma | \bar{x} \gamma = \beta_{ATE}) + c_i \E(\bar{x} \gamma | \bar{x} \gamma = \beta_{ATE}) \\
								   & = \E((x_{i} - c_i \bar{x}) \gamma | \bar{x} \gamma = \beta_{ATE}) + c_i \beta_{ATE}                                       \\
				\end{align*}
				For any constant $c_i$. \\
				Choose $c_i$ so that 
				\begin{align*}
					\Cov((x_{i} - c_i \bar{x})\gamma, \bar{x} \gamma) = 0
				\end{align*} 
				Assume normality so that this guarantees independence.
				Then,
				\begin{align*}
					\E((x_i - c_i \bar{x}) \gamma | \bar{x} \gamma = \beta_{ATE}) = (x_{i} - c_i \bar{x}) \E(\gamma)
				\end{align*}
				So then
				\begin{align*}
					(x_i - c_i \bar{x}) \E(\gamma) + c_i \beta_{ATE} = x_i \E(\gamma) + c_i (\beta_{ATE} - \bar{x} \E(\gamma))
				\end{align*} 
				($c_i$ depends on $x_i$)

				In other words, your belief is your prior, adjusted based on the difference between the observed ATE and your prior about the ATE.
				The key question is how much adjustment you do which depends on $"c_i"$. We choose $c_i$ to solve:

				\begin{align*}
                          & \Cov ((x_i - c_i \bar{x}) \gamma, \bar{x} \gamma) = 0                          \\
				 \iff     & \Cov(x_i \gamma, \bar{x} \gamma) -c_i \Cov(\bar{x} \gamma, \bar{x} \gamma) = 0 \\
					\iff  & \Cov(x_i \gamma, \bar{x} \gamma) = c_i \Var(\bar{x} \gamma)                  \\
				\iff & c_i = \frac{\Cov(\beta_i, \beta_{ATE}) }{ \Var(\beta_{ATE})}
				\end{align*} 
				The random variable in this context is $\gamma$ (the coefficients on the $x $'s) in this case $\Var(\beta_{ATE})$ is a measure of how uncertain one was about what $\beta_{ATE}$ would be before doing the trial.

				$c_i$ is the equation for a regression of $\beta_i$ on $\beta_{ATE}$. In other words, we take a bunch of patients with characteristics $x_i$ and we keep redrawing the gammas from our prior distribution. Then we ask how correlated  $\beta_i$ and $\beta_{ATE}$ are. If they are more correlated (as they would be for patients where the $x_i$ are closer to $\bar{x}$) we update more.

				To compute $c_i$, we just need to know $x_i$, $\bar{x}$, and the distribution of $\gamma$.

				Suppose we want to design the trial to minimize:
				\begin{align*}
					\min \E[(\beta_i - \beta_{i,post})^2]
				\end{align*} 
		\end{enumerate}

\end{enumerate} 


% First observe that in our current setup, we have that
% \begin{align*}
% 	c = \frac{\Cov ( \gamma_0 + \gamma_1 x , \gamma_0  + \gamma_1 \bar{x} )}{ \Var( \gamma_0  + \gamma_1 \bar{x} ))}
% \end{align*} 


% so for individual i, $c$ reduces to

% \begin{align*}
% 		c &= \frac{\Var(\gamma_0) + (x + \bar{x}) \Cov(\gamma_0, \gamma_1) + x \bar{x} \Var(\gamma_1)}{\Var(\gamma_0) + 2 \bar{x} \Cov(\gamma_0, \gamma_1) + \bar{x}^2\Var(\gamma_1)} \\
% 		C_{women} &= \frac{\Var(\gamma_0) + \bar{x} \Cov(\gamma_0, \gamma_1)}{\Var(\gamma_0) + 2 \bar{x} \Cov(\gamma_0, \gamma_1) + \bar{x}^2\Var(\gamma_1)} \\
% 	C_{men} &= \frac{\Var(\gamma_0) + (1 + \bar{x}) \Cov(\gamma_0, \gamma_1) + \bar{x} \Var(\gamma_1)}{\Var(\gamma_0) + 2 \bar{x} \Cov(\gamma_0, \gamma_1) + \bar{x}^2\Var(\gamma_1)} \\
% \end{align*} 

